Subsegmental language detection in Celtic language text

### 2014-07-02 codeswitch-cltw-2014/codeswitch_camera_ready.tex
included email and removed small
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55179 72bbbca6-d526-0410-a7d9-f06f51895060

\author{}
\author{Akshay Minocha \\
  IIIT Hyderabad  \\
  Hyderabad (India) \\
  {\small {\tt akshay.minocha@students.iiit.ac.in}} \\\And
  Francis M. Tyers \\
  Giellatekno \\ %/CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\small {\tt francis.tyers@uit.no}} \\}

>>>>

\author{}
\author{Akshay Minocha \\
  IIIT Hyderabad  \\
  Hyderabad (India) \\
  {\tt akshay.minocha@students.iiit.ac.in} \\\And
  Francis M. Tyers \\
  Giellatekno \\ %/CLEAR \\
  UiT Norgga \'arktala\v{s} universitehta  \\
  9017 Romsa (Norway) \\
  {\tt francis.tyers@uit.no} \\}
